Gaps in stellar streams as a result of globular cluster fly-bys

### 2024-12-02 paper/main.tex
paragraph for the conclusion

\section{Conclusions}
  Our study demonstrates that globular cluster flybys can produce density gaps in the stellar streams of clusters like Palomar 5, but the occurrence and characteristics of these gaps depend heavily on the dynamical and structural properties of the stream and the Galactic environment. While our simulations predict the formation of gaps in Palomar 5's tails, the predicted gaps do not align with the regions of the stream currently observed. This discrepancy highlights the challenges in reconciling theoretical predictions with observational data, particularly given the complex interplay between orbital dynamics, stream structure, and the nature of close encounters.

>>>>

\section{Conclusions}
  Our study demonstrates that globular cluster flybys can produce density gaps in the stellar streams of Palomar~5, but the occurrence and characteristics of these gaps depend heavily on the dynamical and structural properties of the stream and the Galactic environment. While our simulations predict the formation of gaps in Palomar~5's tails, the predicted gaps do not align with the regions of the stream currently observed. This discrepancy highlights the challenges in reconciling theoretical predictions with observational data, particularly given the complex interplay between orbital dynamics, stream structure, and the nature of close encounters.
